% main_example.tex — Laurel electronic press kit (EPK) / one-sheet
% Compile:  pdflatex main_example.tex
% Targets pdflatex (standard TeX Live). Lato is used if installed, else the default face.
% /submit fills the placeholders from materials/PROFILE.md and saves a tailored copy to
% submissions/<festival-slug>/press-kit.tex
\documentclass[11pt,a4paper]{article}

\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage[margin=0.9in]{geometry}
\usepackage{parskip}
\usepackage{xcolor}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\IfFileExists{lato.sty}{\usepackage[default]{lato}}{}

\definecolor{accent}{HTML}{F4530E}
\definecolor{ink}{HTML}{1C2029}
\definecolor{dim}{HTML}{5C616B}
\color{ink}
\pagestyle{empty}

% Section headings: small, tracked, accent rule
\titleformat{\section}{\bfseries\large\color{ink}}{}{0em}{}[{\color{accent}\titlerule[1.5pt]}]
\titlespacing*{\section}{0pt}{1.2em}{0.5em}

% ── Film facts (edit these) ─────────────────────────────────────────
\newcommand{\filmtitle}{THE SALT ROAD}
\newcommand{\filmlogline}{A teenage smuggler inherits her estranged father's debt --- and the
desert route that comes with it.}

\begin{document}

% ── Title block ──
{\fontsize{30}{32}\selectfont\bfseries \filmtitle}\par
\vspace{0.2em}{\color{accent}\rule{4cm}{2.5pt}}\par
\vspace{0.6em}{\large\itshape \filmlogline}\par
\vspace{0.4em}{\color{dim}\small Feature \textbar\ 94 min \textbar\ Drama \textbar\ 2026 \textbar\ Mexico/USA \textbar\ Spanish, English}\par

\section*{}
\section{Synopsis}
\textbf{Short.} Replace with an 80--120 word synopsis: the world, the protagonist, the central
tension. Do not spoil the third act.

\medskip
\textbf{Long.} Replace with a 200--300 word synopsis covering the fuller arc, still avoiding the
ending unless the festival explicitly asks for it.

\section{Director's statement}
First person, ~150--250 words: why this film, the central creative choice, and what you want it to
do for an audience. Honest and personal --- not a sales pitch.

\section{Director}
\textbf{Name.} 60--100 word bio: prior work and where it played, training, and the throughline of
your work. Only real credits.

\section{Key cast \& crew}
\begin{itemize}[leftmargin=1.2em,nosep]
  \item \textbf{Written \& directed by} ---
  \item \textbf{Produced by} ---
  \item \textbf{Cinematography} ---
  \item \textbf{Editing} ---
  \item \textbf{Lead cast} ---
\end{itemize}

\section{Technical specifications}
\begin{itemize}[leftmargin=1.2em,nosep]
  \item \textbf{Runtime:} 94 min \quad \textbf{Format:} DCP / ProRes \quad \textbf{Aspect:} 2.39:1
  \item \textbf{Sound:} 5.1 \quad \textbf{Language:} Spanish, English (English subtitles)
  \item \textbf{Shooting format:} \quad \textbf{Country:} \quad \textbf{Year:} 2026
  \item \textbf{Premiere status:} World premiere available
\end{itemize}

\section{Contact}
Name --- email --- phone --- website. (Sales/festival contact if different.)

\end{document}
